Luminance constancy under fixed geometry

### 2018-02-12 Draft2/draft2.tex
more edits

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose and the position of the observer (Fig.~\ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

@@

Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
The AMA receptive fields do an excellent job of predicting the target object luminance. The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
The relative error of estimation is $\sim15\%$, which low compared to that of the naive model ($\sim42\%$) or the linear model on center pixel ($\sim21\%$).

@@

Fig.~{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work. The receptive fields are ranked in ascending order of the value of the cost function associated with them. Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost. The L, M and S components give the weights for the linear sum of the cone responses for the three cone types. The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.

@@

% Figure 14
\begin{figure}
\centering
\begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
	\caption{Case 1}
	\label{fig:case1Bar}
    \end{subfigure}
    ~ 
    \begin{subfigure}{0.22 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
	\caption{Case 2}
	\label{fig:case2Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
	\caption{Case 3}
	\label{fig:case3Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
	\caption{Case 4}
	\label{fig:case4Bar}
    \end{subfigure}
\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases. (a) Relative error of the estimates obtained using the linear model and AMA. The AMA receptive fields of case 1, 2 and 3 are used to estimate the target object luminance of the test images from case 1. The AMA receptive fields from all three cases perform well in this case. (b) Relative error for images of case 2. As expected, the error of the linear model on the center pixel is higher than AMA. AMA receptive fields from case 1 do worse than the receptive fields from case 2 and 3. (c) Relative error for images of case 3. The best predictions are from the receptive learnt using the images of case 3.}
 \label{fig:barGraphs}
\end{figure}

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We generated a dataset of multispectral images labeled by the reflectance of a target object in each image. These images were generated by a software pipeline developed for this work that we call Virtual world color constancy (VWCC). This software creates 3D scene descriptors based on programatic information provided by the user. Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc. We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances. Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image. Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.

In this paper, as a first step towards understanding color constancy using supervised methods on labeled dataset, we studied a simpler analogue: luminance constancy. We generated images labeled with the luminance of a target object in the scene. We performed three types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:studiedCases}). 1. Allow variations in the spectral shape of the target object surface reflectance spectrum, while keeping the background object surface reflectance and the illumination spectra of the light sources fixed. 2. Allow variations in the shape of the target object surface reflectance and the illumination spectra of the light sources, while keeping the surface reflectance spectra of the background objects fixed. 3. Allow variations in all three types of spectra. We generated hundreds of images at multiple luminance level of the target object for each of these three cases. Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database. These model retinal responses, along with the luminance label of the images, are then used as the input to supervised learning algorithms. Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra. In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects. When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.

>>>>

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

@@

Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 4. 
We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
The AMA receptive fields do an excellent job of predicting the target object luminance. The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
The relative error of estimation is $\sim15\%$, which low compared to that of the naive model ($\sim42\%$) or the linear model on center pixel ($\sim21\%$).

@@

Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work. The receptive fields are ranked in ascending order of the value of the cost function associated with them. Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost. The L, M and S components give the weights for the linear sum of the cone responses for the three cone types. The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.

@@

% Figure 14
\begin{figure}
\centering
\begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
	\caption{Case 1}
	\label{fig:case1Bar}
    \end{subfigure}
    ~ 
    \begin{subfigure}{0.22 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
	\caption{Case 2}
	\label{fig:case2Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
	\caption{Case 3}
	\label{fig:case3Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
	\caption{Case 4}
	\label{fig:case4Bar}
    \end{subfigure}
\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases. Each panel shows the relative error of the estimates obtained using the linear model and the AMA receptive fields of case 1-4. (a) Relative error of estimates of the target object luminance of images from case 1. The AMA receptive fields from all three cases perform well in this case. (b) Relative error for images of case 2. As expected, the error of the linear model on the center pixel is higher than AMA. As expected, the best estimates are provided by the receptive fields of case 2. (c) Relative error for images of case 3. (d) Relative error for test images of case 4.}
 \label{fig:barGraphs}
\end{figure}

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We generated datasets of multispectral images labeled by the reflectance of a target object in each image. The images were generated using a software pipeline developed for this work that we call Virtual world color constancy (VWCC). The software creates 3D scene descriptors based on programatic information provided by the user. Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc. We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances. Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image. Such databases are nearly impossible to generate for natural scenes as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab. We used these labeled images in a supervised manner to understand the computations required for estimating the luminance of an object under spectral variations in the scene.

In this work, as a first step towards understanding luminance constancy, we generated images labeled with the luminance of a target object. We performed four types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:introExampleFigure}-\ref{fig:studiedCases}). 1. variations in the surface reflectance spectrum of the target object, 2. variations in surface reflectance spectrum of both target and the background objects, 3. variations in the surface reflectance spectrum of the target and the emission spectrum of the light source, and 4. variation is surface reflectance spectrum of the target and the background objects and the emission spectrum of the light source. We generated hundreds of images at multiple luminance level of the target object for each of these cases. Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database. These model retinal responses, along with the luminance label of the images, were then used as the input to supervised learning algorithms. Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra. In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects. When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.

Summary

Effect of background. multiple reflection

center surround RFs

LM
